Output Summary

### 2022-06-16 03-post-process/output-plots.Rmd

```{r directories, include = F}
# set root directory to the project directory: one level up from this location
knitr::opts_knit$set(root.dir = "../")
```

@@

# load packages
source("00-packages.R")

# load all necessary functions
invisible(sapply(list.files(path = "01-functions", pattern = "\\.R$", full.names = T), source))

# set the input directory
in_dir = "02-model/model-output"

>>>>

```{r directories, include = F}
# set root directory to the project directory: one level up from this location
# knitr::opts_knit$set(root.dir = "../")
```

@@

# load packages
source("../00-packages.R")

# load all necessary functions
invisible(sapply(list.files(path = "../01-functions", pattern = "\\.R$", full.names = T), source))

# set the input directory
in_dir = "../02-model/model-output"
